### 2023-09-03 sections/5-discussion.tex
changes to rnn
comment about poor recall on cosine

@@

Additionally, we would like to implement additional distance functions to improve the genericity of CAKES. 
For example, we would like to implement Tanimoto Distance using maximal-common-subgraph for molecular structures. Ultimately, 
we would also like to implement Wasserstein distance for dimensions higher than 2. In order to make this possible, 
we plan to implement GPU-acceleration for the more computationally-intensive distance functions like Wasserstein.

>>>>

While CAKES has perfect recall for distance metrics, it exhibits worse recall under non-metrics (specifically, cosine distance). This bears further investigation, but likely stems from how heavily the knn and clustering algorithms depend on the triangle inequality.

@@

Additionally, we would like to implement additional distance functions to improve the genericity of CAKES. 
For example, we would like to implement Tanimoto Distance using maximal-common-subgraph for molecular structures. Ultimately, 
we would also like to implement Wasserstein distance for dimensions higher than two. In order to make this possible, 
we plan to implement GPU-acceleration for the more computationally-intensive distance functions like Wasserstein.
